Verifying Demonstrations

### 2019-05-02 paper/MANETs.tex

We also need the participants to communicate during the protest.
Since the cellular network could be shut down to keep protesters from accessing 
the Internet, making phone calls or texting, we require a different means of 
communications between protesters. This could be accomplished by Bluetooth or 
WiFi communications, as demonstrated by Briar~\cite{Briar} and 
FireChat~\cite{FireChat}, two examples of applications for communication during 
protests via wireless mesh networking. The crowd-counting scenario likely has 
higher requirements on capacity and withstanding interference as the 
participants continuously run the protocol for witnessing each others presence; 
messages are presumably less frequent. 5G is intended to cope with billions of 
devices (IoT), and thus could help cope with the device density in crowds.
An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
Specifically, the out-of-band and autonomous version D2D would fit our
scenario thanks to using unlicensed spectrum and working without
cellular coverage. Due to the requirements of lawful intercept and the
drive for operators to identify the network users, there still is an
authorization step to communicate in this mode.
%~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

>>>>

We need the participants to communicate during the protest.
Since the cellular network could be shut down to keep protesters from accessing 
the Internet, making phone calls or texting, we require a different means of 
communications between protesters. This could be accomplished by Bluetooth or 
WiFi communications, as demonstrated by Briar~\cite{Briar} and 
FireChat~\cite{FireChat}, two examples of applications for communication during 
protests via wireless mesh networking. The crowd-counting scenario likely has 
higher requirements on capacity and withstanding interference as the 
participants continuously run the protocol for witnessing each others presence; 
messages are presumably less frequent. 5G is intended to cope with billions of 
devices (IoT), and thus could help cope with the device density in crowds.
An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
Specifically, the out-of-band and autonomous version D2D would fit our
scenario thanks to using unlicensed spectrum and working without
cellular coverage. Due to the requirements of lawful intercept and the
drive for operators to identify the network users, there still is an
authorization step to communicate in this
mode. Near-field-communication (NFC) would
solve any scalability problem from interference, require no
infrastructure or provider, but at the price of having
participant and witness hold their phones together for each proof
share. 
%~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

### 2019-05-02 paper/adversary-model.tex

% We now provide a concretely defined system and adversary model.
% We give three definitions, each defining an adversary with increasingly stronger 
% capabilities (\ie more auxiliary information).

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the adversary model.
    The protester (with real identity) \(P\) and witness (with real identity) 
    \(W\) communicate.
    They exchange protocol data as a function~\(d\) of the protest and 
    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
    \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the 
    adversary.
  }
\end{figure}

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(S\).
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}

This adversary has no access to data from outside the system, \eg inferences 
that can be made from the communication layer (\eg IP-addresses mapped to 
physical identities or face recognition from the protest), which means that it 
has only the protocol data at its disposal.

>>>>

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\), and a ledger~\(\TS\) (\ie time-stamping storage, that will 
contain the set of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and record when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(\TS\) and \(\TS\) only learns 
some function \(f\) of the protocol data exchanged with the witness,
\(f(d_{P,W}(\cid, P))\), and the time of the 
communication (\(t_{P,\TS}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the adversary model.
    The protester (with real identity) \(P\) and witness (with real identity) 
    \(W\) communicate.
    They exchange protocol data as a function~\(d\) of the protest and 
    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
    \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the ledger \(\TS\), who records the time that happened, \(t_{P,\TS}\).
    %Both the witness \(W\) and the ledger \(\TS\) are controlled by the 
    %adversary.
  }
\end{figure}

The adversary maliciously controls \(W\) (the strongest role a
participant can take on).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
like everyone else (\ie a malicious protester~\(P\)).
The adversary only learns the protocol data, \ie what is sent over the 
channel --- no auxiliary data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.

### 2019-05-02 paper/conclusions.tex

We showed that \CROCUS provides universally verifiable data.
With \CROCUS, a journalist can easily count the participation, specify how they 
counted (time, location \etc) along with the result and everyone can 
independently verify that the result is correct.
The only results that cannot be trusted are results aligned with the interests 
of the \ac{CA}.

@@

% In general, none of the related works fulfills the eligibility
% verifiability (one proof per person, temporal and spatial eligibility ---
% \cref{%
%   CountOnce,%
%   TemporallyRelated,SpatiallyRelated,%
% }).
% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
% Moreover, if they provided individual verifiability, they would likely violate 
% the privacy requirements --- if people must recognize themselves in photos, 
% others can recognize them too.
% Finally, most of the current methods are estimates, with quite some error margins. 
While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the flip side of the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and increase transparency.

>>>>

We showed that \CROCUS provides universally verifiable data.
With \CROCUS, a journalist can easily count the participation, specify how they 
counted (time, location \etc) along with the result and everyone can 
independently verify that the result is correct.
The only results that cannot be trusted are results aligned with the interests 
of the \ac{CA} (which can be mitigated by multi-party solutions).

@@

% In general, none of the related works fulfills the eligibility
% verifiability (one proof per person, temporal and spatial eligibility ---
% \cref{%
%   CountOnce,%
%   TemporallyRelated,SpatiallyRelated,%
% }).
% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
% Moreover, if they provided individual verifiability, they would likely violate 
% the privacy requirements --- if people must recognize themselves in photos, 
% others can recognize them too.
% Finally, most of the current methods are estimates, with quite some error margins. 
While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Until used by most participants, \CROCUS would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and increase transparency.

### 2019-05-02 paper/identity-limits.tex

The most widely deployed identity system is that of nation states: in essence, 
an identity is created at birth in the form of the equivalent of a birth 
certificate\footnote{%
  Many countries issue birth certificates, but there are other, equivalent, 
  ways.
  \Eg Sweden does not issue birth certificates, it simply creates and entry in 
  the population registry.
} This birth certificate later serves as the root for many authentication 
mechanisms, \eg national identity cards and passports.
Although this seems centralized at first glance, as we will see below, it is 
indeed comparable in decentralization to distributed ledgers due to audit 
trails and separation of duties.
As we will see, the problem with this system is that its federated structure 
and reliance on audit trails fails when it comes to issuing a 
privacy-preserving attribute-based credential for identity (or physical 
person).

@@

An identity is created when an entry is made in the population registry.
Each entry in the registry has a unique identification number.
The population registry serves various purposes, one, arguably among the most 
important, is the generation of the electoral 
roll~\cite{Valmyndigheten-ElectoralRoll}.

For a person to cause an entry into the population registry, they have two 
options:
they are in the population registry and give birth to a child, or
they were born abroad and apply to immigrate to Sweden.

In the case of a birth\footnote{%
  Technically, this is the procedure if the child is born abroad.
  If the child is born in Sweden, the hospital will report all these things 
  directly to the population registry without issuing any papers to the 
  parents.
} they need:
\begin{itemize}
  \item passports, to prove the identities of the parents;
  \item a birth certificate where the names of the parents are present;
  \item a pregnancy certificate, to prove who birthed the child;
  \item a certificate of who the father is~\cite{Skatteverket-RegisterBirth}.
\end{itemize}
So the security is reduced to the forgeability of these items.

Obviously the one who creates entries in the population registry can do that 
even without such documents, so there must be some separation of duty, audit 
trail or transparency to prevent the agency from performing a Sybil attack.
In the case of Sweden, the population registry is public.
This means that in addition to any audit trail in place at the agency, we have 
these properties:
\begin{itemize}
  \item The data must fulfil correctness: a person must have parents, who in 
    turn must have parents, \etc.
  \item Anyone can detect extraordinary additions, \eg exceptionally many 
    births, additions of family trees, \etc.
    Individual women and men would also notice if extra children were added to 
    them (they would receive additional child benefits).
  \item Addition of persons of foreign heritage must have a corresponding audit 
    trail at the Migration Board (separate agency).
\end{itemize}
A foreign citizen can prove their identity to the Migration Board in the 
following ways:
\begin{itemize}
  \item showing a national passport in the original or
  \item showing an identity document in the original or
  \item a close relative attesting to the 
    identity~\cite{Migrationsverket-ProvenIdentity}.
\end{itemize}
Thus the security is reduced to subverting one of these methods.

@@

In Sweden, the identity credential system is federated.
There are several entities that are authorized to issue identity cards; \eg the 
Swedish Tax Agency, the Swedish Police, the banks.
Thus, technically, to detect a Sybil attack by them, \ie fake identities, one 
must check the ID against the population registry and follow the audit trail.
With anonymous credentials, this becomes a problem.

>>>>

The most widely deployed identity system is that of nation states: in essence, 
an identity is created at birth in the form of the equivalent of a birth 
certificate\footnote{%
  Many countries issue birth certificates, but there are other, equivalent, 
  ways.
  \Eg Sweden does not issue birth certificates, it simply creates and entry in 
  the population register.
} This birth certificate later serves as the root for many authentication 
mechanisms, \eg national identity cards and passports.
Although this seems centralized at first glance, as we will see below, it is 
indeed comparable in decentralization to distributed ledgers due to audit 
trails and separation of duties.
As we will see, the problem with this system is that its federated structure 
and reliance on audit trails fails when it comes to issuing a 
privacy-preserving attribute-based credential for identity (or physical 
person).

@@

An identity is created when an entry is made in the population register.
Each entry in the register has a unique identification number.
The population register serves various purposes, one, arguably among the most 
important, is the generation of the electoral 
roll~\cite{Valmyndigheten-ElectoralRoll}.

For a person to cause an entry into the population register, they have two 
options:
they are in the population register and give birth to a child, or
they were born abroad and apply to immigrate to Sweden.

In the case of a birth\footnote{%
  Technically, this is the procedure if the child is born abroad.
  If the child is born in Sweden, the hospital will report all these things 
  directly to the population register without issuing any papers to the 
  parents.
} they need:
\begin{itemize}
  \item passports, to prove the identities of the parents;
  \item a birth certificate where the names of the parents are present;
  \item a pregnancy certificate, to prove who birthed the child;
  \item a certificate of who the father is~\cite{Skatteverket-RegisterBirth}.
\end{itemize}
So the security is reduced to the forgeability of these items.

Obviously the one who creates entries in the population register can do that 
even without such documents, so there must be some separation of duty, audit 
trail or transparency to prevent the agency from performing a Sybil attack.
In the case of Sweden, the population register is public.
This means that in addition to any audit trail in place at the agency, we have 
these properties:
\begin{itemize}
  \item The data must fulfil correctness: a person must have parents, who in 
    turn must have parents, \etc.
  \item Anyone can detect extraordinary additions, \eg exceptionally many 
    births, additions of family trees, \etc.
    Individual women and men would also notice if extra children were added to 
    them (they would receive additional child benefits).
  \item Addition of persons of foreign heritage must have a corresponding audit 
    trail at the Migration Board (separate agency).
\end{itemize}
A foreign citizen can prove their identity to the Migration Board in the 
following ways:
\begin{itemize}
  \item showing a national passport in the original or
  \item showing an identity document in the original or
  \item a close relative attesting to the 
    identity~\cite{Migrationsverket-ProvenIdentity}.
\end{itemize}
Thus the security is reduced to subverting one of these methods.

@@

In Sweden, the identity credential system is federated.
There are several entities that are authorized to issue identity cards; \eg the 
Swedish Tax Agency, the Swedish Police, the banks.
Thus, technically, to detect a Sybil attack by them, \ie fake identities, one 
must check the ID against the population register and follow the audit trail.
With anonymous credentials, this becomes a problem.

### 2019-05-02 paper/related-work.tex

\subsection{Crowd counting methods}
\input{crowd-counting-methods.tex}

\subsection{Location proofs}
\input{location-proofs.tex}

>>>>

%\subsection{Crowd counting methods}

The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count. Using pictures makes it difficult to get cumulative counts, verify that the pictures have not been manipulated, and to have both privacy and individual verifiability: either one is included in the picture (privacy problem) or not (verifiability problem). Similar limitations exist for estimating the number of persons in a picture or video (\eg the work of \cite{NNCrowdCounting} or  CrowdSize~\cite{CrowdSize}).

Another problem for all the above methods is exemplified by the demonstrations in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
}.
In this situation it is very difficult to faithfully capture the situation.
Taking pictures from different angles risks double counts. Another challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.

Counting MAC addresses, as done by a company during the protests in Seoul~\cite{2016DemonstrationsInSeoul} suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.

An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}. 
This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.

CrowdCount \citet{CrowdCount} is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.

%\input{location-proofs.tex}

### 2019-05-02 paper/system-model.tex

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
  The \ac{CA} can be centralized or decentralized, but as 
  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
    centralized} to prevent Sybil attacks.
  See \cref{identity-limits} for a discussion on existing identity systems and 
  their limits.
} that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every identity there exists at most one valid digital certificate.
}.

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries and computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.

@@

We draw inspiration from properties for voting systems as formalized
in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
\end{description}

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital identity certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
  The \ac{CA} can be centralized or decentralized, but as 
  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
    centralized} to prevent Sybil attacks.
 } that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every physical person there exists at most one valid digital certificate.
}.

In practice, participants witness each other's participation using
their smartphones (or similar devices) running the protocol described
in \cref{Protocol} and uploading their testimony (\ie, proof shares)
to a ledger (such as a blockchain) after the protest.  During the
protest, the devices might be limited by their batteries and
computations they can perform and only have local connectivity to each
other.  No connection to any global network such as the Internet is
necessary at that time.  Nonetheless, before and after the protest, we
assume that the devices have global connectivity (\ie Internet
connections) and are not computationally limited by any battery, for
the participants to be able to upload their proof shares to the
ledger.

@@

We draw inspiration from properties for voting systems as formalized
in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
\end{description}

### 2019-05-02 paper/timestamp.tex

We need a robust time-stamping and storage service (\ie a ledger), \(\TS\), 
which implements the following oracles:
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\) such that 
    \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSsubmit[x]\) stores \(x\) permanently and yields a value 
    \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and 
    \(\TStime[\pi] = t\).
\end{itemize}

@@

We require a few additional properties from \(\TS\) that are already provided 
by ledgers.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which 
blocks are created every 10 minutes on average (this is so that \(\TStime\) can 
map values from \(\TSget\) to real time).
Second, \(\TS\) must provide \emph{immutability} and availability to any data 
committed through \(\TSsubmit\) to ensure verifiability of the data by anyone 
at any time.

>>>>

We need a robust time-stamping and storage service (\ie a ledger), \(\TS\), 
which implements the following:
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\) such that 
    \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSsubmit[x]\) stores \(x\) permanently and yields a value 
    \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and 
    \(\TStime[\pi] = t\).
\end{itemize}

@@

We require a few additional properties from \(\TS\) that are already provided 
by ledgers.
First, \(\TS\) must be continuously extended, such as in the Bitcoin blockchain in which 
blocks are created every 10 minutes on average (this is so that \(\TStime\) can 
map values from \(\TSget\) to real time).
Second, \(\TS\) must provide \emph{immutability} and availability to any data 
committed through \(\TSsubmit\) to ensure verifiability of the data by anyone 
at any time.

### 2019-05-02 paper/verifiability-analysis.tex

\subsubsection{Linkability}%
\label{analysis-linkability}

@@

Forging a witness's signature on a proof is equivalent to breaking linkability 
above (\cref{analysis-linkability}).
As above, this is reduced to the security of the \(\AC\) scheme.

Finally, Alice can corrupt witnesses.
In the case of trusted witnesses, Alice's chance of corrupting witnesses is 
reduced to the trustworthiness of the witnesses chosen by the verifier.
In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
succeeds only if she can corrupt at least \(\theta\) witnesses.

@@

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger~\(\TS\) 
and available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger (\cf \cref{timestamp}).

@@

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger; but universal verifiability also 
depends on the eligibility verification (each proof must be verified as 
eligible to count).

>>>>

\subsubsection{Counted only once}%
\label{analysis-linkability}

@@

Forging a witness's signature on a proof is equivalent to breaking the 
counted-only-once property 
above (\cref{analysis-linkability}).
As above, this is reduced to the security of the \(\AC\) scheme.

Finally, Alice can corrupt witnesses.
In the case of trusted witnesses, Alice's chance of corrupting witnesses is 
reduced to the trustworthiness of the witnesses chosen by the verifier.
In the \(\theta\)-threshold case, with unknown witnesses, 
%(by assumption) 
Alice succeeds only if she can corrupt at least \(\theta\) witnesses.

@@

\Cref{IndividualVerif} means that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger~\(\TS\) 
and available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger (\cf \cref{timestamp}).

@@

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
Like for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger; but universal verifiability also 
depends on the eligibility verification (each proof must be verified as 
eligible to count).
